### 2021-10-06 documentos/vector_space.tex
I'm just a grunt. Don't blame me for this awful PoS.

Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
as
\begin{equation}
\san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
= 
\san_{\valpha\vbeta} 
, \quad
\forall \vec\beta\in\Phi(\vec\alpha),
\label{eq:12}
\end{equation}
which can be further decomposed in 
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
  \ldots
%   \cdot\ldots\cdot 
\sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
\sa_{\alpha_1\beta_1}
  \ldots
% \cdot\ldots\cdot
 \sa_{\alpha_N\beta_N}.
\label{eq:13}
\end{equation}
% Moreover, since 
% 
% 
% 
% Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
% \label{eq:12}
% \end{equation}
% This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
% (\ref{eq:12}) may be rewritten as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
% \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
% \label{eq:13}
% \end{equation}
Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
the above relation must hold individually for every index\cpnote{francois, recuerdo 
que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
proque se tiene que cumplir para los indices individulaes}. Thus we have, 
that, for all $1\leq k\leq N$, $\gamma_k$
and $\gamma_k^\prime$ are connected by
\begin{equation}
\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
\label{eq:14}
\end{equation}
for all $0\leq\beta\leq3$. This is equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha\oplus{}\gamma_k
\label{eq:15}
\end{equation}
where the $\oplus{}$ operation is defined by (\ref{eq:14}). See Figure
\ref{tab:1} for a detailed description. \cpnote{by direct calculation I can verify 
that its true, but I see it as a coincidence. Is they ere a say to know
that \eref{eq:14} will lead to a sum?}

@@

Note further that if we perform the identification
\begin{subequations}
\begin{eqnarray}
0&\to&(0,0)\label{eq:identa}\\
1&\to&(0,1)\label{eq:identb}\\
2&\to&(1,0)\label{eq:identc}\\
3&\to&(1,1)\label{eq:identd}
\end{eqnarray}
\label{eq:ident}
\end{subequations}
then the $\oplus$ operation reduces to simple vector addition in
binary arithmetic. If we therefore denote by $\overline{\alpha}$
\cpnote{I dont think this is necesary. specially if we will write something
else}
the multi-index $\vec\alpha$ converted to a binary vector by the componentwise
application of (\ref{eq:ident}),
the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
as
\begin{equation}
\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
\label{eq:17}
\end{equation}
where the addition sign here refers to ordinary binary vector addition.

>>>>

Since all elements of $A$ are $\pm1$, and using that $A_{\valpha \vbeta}=1$
of $\vbeta \in \Phi(\vec\alpha)$, we may rewrite \eref{eq:coneccion:dos:indices:A}
as
\begin{equation}
\san_{\vbeta\vec\gamma} \san_{\vbeta\vec{\gamma^\prime}} 
= 
\san_{\valpha\vbeta} 
, \quad
\forall \vec\beta\in\Phi(\vec\alpha),
\label{eq:12}
\end{equation}
which can be further decomposed in 
\begin{equation}
\sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}
  \ldots
%   \cdot\ldots\cdot 
\sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
\sa_{\alpha_1\beta_1}
  \ldots
% \cdot\ldots\cdot
 \sa_{\alpha_N\beta_N}.
\label{eq:13}
\end{equation}
% Moreover, since 
% 
% 
% 
% Since $\sa_{\alpha\beta}=\pm1$, we may rewrite (\ref{eq:11}) as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=1.
% \label{eq:12}
% \end{equation}
% This must hold for all $\vec\beta\in\Phi(\vec\alpha)$. From this follows that
% (\ref{eq:12}) may be rewritten as
% \begin{equation}
% \sa_{\beta_1\gamma_1}\sa_{\beta_1\gamma_1^\prime}\cdot\ldots\cdot \sa_{\beta_N\gamma_N}\sa_{\beta_N\gamma_N^\prime}=
% \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}.
% \label{eq:13}
% \end{equation}
Since this must hold for all $\vec\beta\in\Phi(\vec\alpha)$, it follows that 
the above relation must hold individually for every index\cpnote{francois, recuerdo 
que esto lo discutimos. No se si en el momento me convencí, pero ahora no veo 
proque se tiene que cumplir para los indices individulaes}. Thus we have, 
that, for all $1\leq k\leq N$, $\gamma_k$
and $\gamma_k^\prime$ are connected by
\begin{equation}
\sa_{\beta\gamma_k}\sa_{\beta\gamma_k^\prime}=\sa_{\beta\alpha}
\label{eq:14}
\end{equation}
for all $0\leq\beta\leq3$. One can verify, by working out the different cases, 
that \eref{eq:14} equivalently expressed as 
\begin{equation}
\gamma_k^\prime=\alpha\oplus{}\gamma_k
\label{eq:15}
\end{equation}
where the $\oplus{}$ denotes the operation of the Kein group; see Figure
\ref{tab:1} for a detailed description. 
% \cpnote{by direct calculation I can verify 
% that its true, but I see it as a coincidence. Is they ere a say to know
% that \eref{eq:14} will lead to a sum?}

\cpnote{
It will be useful to think of the multi-index $\valpha$ as an element of 
a vector space. To do so, we notice that any group with the property that
$\alpha \oplus \alpha =0$ is indeed a vector space under the two-element field
$\{0,1\}$\cite{alguna:referencia}.  Then, we build the complete vector space,
with the same field, and defining $\valpha \oplus \vbeta = (\alpha_1 \oplus
\beta_1,\cdots, \alpha_N \oplus \beta_N)$. From this view 
we can derive several interesting observations that will be presented in 
the rest of the section. 
}

@@

\cpnote{Propongo quitar desde aca}
Note further that if we perform the identification
\begin{subequations}
\begin{eqnarray}
0&\to&(0,0)\label{eq:identa}\\
1&\to&(0,1)\label{eq:identb}\\
2&\to&(1,0)\label{eq:identc}\\
3&\to&(1,1)\label{eq:identd}
\end{eqnarray}
\label{eq:ident}
\end{subequations}
then the $\oplus$ operation reduces to simple vector addition in
binary arithmetic. If we therefore denote by $\overline{\alpha}$
\cpnote{I dont think this is necesary. specially if we will write something
else}
the multi-index $\vec\alpha$ converted to a binary vector by the componentwise
application of (\ref{eq:ident}),
the connection between $\vec\alpha$, $\vec\gamma$, and $\vec{\gamma^\prime}$ defined by (\ref{eq:11}) is rewritten 
as
\begin{equation}
\overline\gamma=\overline\alpha+\overline{\gamma^\prime}
\label{eq:17}
\end{equation}
where the addition sign here refers to ordinary binary vector addition. 
\cpnote{Hasta aca}
